Extended Data

### 2021-09-17 doc/manuscript/Dow_Extended_Data.Rmd
minor

growth_curves_all_caption  <- " Extended Data Figure 2 | Growth trajectories for ring- and diffuse-porous trees, as both relative and cumulative fractions of total annual growth. Each line represents one year's growth for a given tree, fit with McMahon model. " #needs wordsmithing!!!

climwin_caption <- "Extended Data Figure 3 | Landscapes of relationships between the day of year on which 25% of annual growth is achieved ($DOY_{25}$) and temperature in prior weeks for ring- and diffuse-porous trees at SCBI and Harvard Forest. Shown are matrices of linear coefficients of first-order linear regressions between temperature and $DOY_{25}$, where Window Open and Window Close indicate number of weeks prior to $DOY_{25}$ (ring-porous: May 5 at SCBI, May 13 at HF; diffuse-porous: June 4 at SCBI, June 14 at HF). Black circles indicate the critical $T_{max}$ window (ring-porous:  March 22- April 9 at SCBI, April 2 - May 07 at HF; diffuse-porous: Feb. 19- May 21 at SCBI, March 19 - May 07 at HF)." #info subject to change!!!

>>>>

growth_curves_all_caption  <- " **Extended Data Figure 2 | Growth trajectories for ring- and diffuse-porous trees, as both relative and cumulative fractions of total annual growth.** Each line represents one year's growth for a given tree, fit with McMahon model. " #needs wordsmithing!!!

climwin_caption <- "**Extended Data Figure 3 | Landscapes of relationships between the day of year on which 25% of annual growth is achieved ($DOY_{25}$) and temperature in prior weeks for ring- and diffuse-porous trees at SCBI and Harvard Forest.** Shown are matrices of linear coefficients of first-order linear regressions between temperature and $DOY_{25}$, where Window Open and Window Close indicate number of weeks prior to $DOY_{25}$ (ring-porous: May 5 at SCBI, May 13 at HF; diffuse-porous: June 4 at SCBI, June 14 at HF). Black circles indicate the critical $T_{max}$ window (ring-porous:  March 22- April 9 at SCBI, April 2 - May 07 at HF; diffuse-porous: Feb. 19- May 21 at SCBI, March 19 - May 07 at HF)." #info subject to change!!!
